\cvsection{Experience}
    \begin{cvtable}
        \cvitem{11, 2020 -- 01, 2021}{\color{cvsectioncolor}Consultant Developer}{\textbf{ILO Consultor, CL}}{I developed an automated web scraping solution in Python B4s to capture data from public job portals, which allowed the company to obtain valuable information about the labour market.}
        \cvitem{07, 2019 -- 01, 2020}{\color{cvsectioncolor}SAPUI5 -IoT Consultant}{\textbf{SCLOUD, CL}}{I designed and developed IoT prototypes, a customized dashboard for a client in the wine industry using technologies such as ESP32 and SAPUI5. This improved the efficiency of their production process and enabled them to make informed decisions in real time.}
        \cvitem{05, 2016 -- 11, 2017}{\color{cvsectioncolor}Development Engineer}{\textbf{Karibu, CL}}{I developed a desktop point-of-sale system using Java Swing and SQL, which improved the efficiency of operations and optimized sales tracking. I also implemented the use of Jasper reporting, which facilitated the monitoring and analysis of sales data.}
        \cvitem{06, 2015 -- 02, 2016}{\color{cvsectioncolor}QA, Testing}{\textbf{Analyze, CL}}{I performed software testing with Pytest and created user manuals to improve the end-user experience at an agricultural company. I identified and documented over 30 critical bugs in the software, which allowed the company to fix them before product release, saving time and money in the correction process.}
    \end{cvtable}
%\input{LANG/EN/experience.tex}
\cvsection{Education}
\subsection{IT}
%\input{LANG/EN/education.tex}
\begin{cvtable}
    \cvitemmedium{02, 2023}{\href{https://github.com/dadapunk/CV-Latex/raw/main/Certificates/IronHackJavaBackEnd_2023.PDF}{\color{cvsectioncolor}\small BackEnd Development Bootcamp (Java SpringBoot)}}{\textbf{IronHack}}
    \cvitemmedium{11, 2022}{\href{https://www.credly.com/badges/a43cfd6e-2c81-4bfe-9762-78a0256abf19/public_url}{\color{cvsectioncolor}\small Google IT Support}}{\textbf{Coursera}}
    \cvitemmedium{11, 2022}{\href{https://s3-us-west-2.amazonaws.com/udacity-printer/production/certificates/6d8cbfdf-2823-4946-a27a-2ebafce69563.pdf}{\color{cvsectioncolor}\small AWS Machine Learning Foundations}}{\textbf{Udacity}}
    \cvitemmedium{12, 2020}{\href{https://www.duoc.cl/wp-content/uploads/2021/10/INGE-INFORMATICA.pdf}{\color{cvsectioncolor}\small Computer Engineering}}{\textbf{DuocUC, Chile}}
    \cvitemmedium{06, 2015}{\href{https://www.duoc.cl/wp-content/uploads/2021/10/ANALISTA-PROG.pdf}{\color{cvsectioncolor}\small Programmer Analyst}}{\textbf{DuocUC, Chile}}
\end{cvtable}
\subsection{Others}
\begin{cvtable}
    \cvitemmedium{05, 2011}{\href{https://www.uchile.cl/carreras/57017/composicion-musical}{\color{cvsectioncolor}\small Music Composition}}{\textbf{Universidad de Chile, Chile}}
    \cvitemmedium{12, 2008}{\href{https://www.uchile.cl/carreras/4954/teoria-de-la-musica}{\color{cvsectioncolor}\small Music Theory}}{\textbf{Universidad de Chile, Chile}}
\end{cvtable}
\profilesection{Short Bio}
\aboutme{Responsible, analytical and methodical IT professional with experience in projects involving different languages, technologies, and architectures (web, mobile, IoT). Experience in building and programming hardware for sound interfaces. I am passionate about the creation and exploration of technological tools that streamline and facilitate processes, improve the quality of life and contribute to a better understanding of our reality.}
\profilesection{Professional goals}
\aboutme{I am looking to further develop my career in technology, exploring new tools and emerging technologies and applying them in innovative projects that have a positive impact on society. I aspire to lead development teams and collaborate with the open source community on relevant projects.}